\documentclass[11.9pt,letterpaper,sans]{moderncv}

\moderncvtheme[black]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8, top=2cm, bottom=2cm]{geometry}


\firstname{\fontsize{40}{42}{\textbf{\textcolor{color1}{Krishn}}}}
\familyname{\fontsize{40}{42}{\textbf{\textcolor{color1}{Ramesh}}}}
\title{\normalsize }%An ambitious collection of nerd particles, passionate techie \& software developer.}
\email{krishnr@gmail.com}
\phone{(226) 979-1174}
\social[linkedin][linkedin.com/in/krishnr]{linkedin.com/in/krishnr}
\social[github][github.com/krishnr]{github.com/krishnr}
\homepage{krishn.me}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% command and color used in this document, independently from moderncv
\definecolor{see}{rgb}{0.5,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts
\renewcommand{\labelitemi}{$\circ$}
%\definecolor{color1}{RGB}{41, 128, 185}
\definecolor{color1}{RGB}{90,150,180}
\definecolor{color2}{rgb}{0.5, 0.5, 0.5}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace*{-1.5cm}

\section{\textbf{Skills}}
		\cvitem{\textbullet}{\textbf{Programming} / Python, JavaScript, Ruby, C++, Matlab, Git}
		\cvitem{\textbullet}{\textbf{Data Science} / Statistics, scikit-learn, basic Machine Learning \& Neural Networks}
		\cvitem{\textbullet}{\textbf{Web Development} / Flask, React, Node.js, Rails, JS (ES6), HTML5, CSS3 \& Sass}
		\cvitem{\textbullet}{\textbf{Design} / Sketch, Photoshop \& Illustrator; keen eye for aesthetic}
		\cvitem{\textbullet}{\textbf{Electronics} / Arduino, circuits, digital systems}
		\cvitem{\textbullet}{\textbf{Passion} / Tech, design, startups, software, electronics, building the future}

\section{\textbf{Experience}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{Winter 2016}{Software Engineer}{\href{http://yelp.com}{Yelp}}{}{}{
			{\footnotesize
				\begin{itemize}
				\item \small Built a high-throughput tracking and logging system for messages using Kafka and Cassandra.
				\item \small Built an automated email system integrated with Salesforce to send and track advertiser emails.
				\end{itemize}
			}
		}
\cventry{Summer 2015}{Full-Stack Developer}{\href{http://pumpup.com}{PumpUp}}{}{}{
			{\footnotesize
				\begin{itemize}
				\item \small Built a grouped notifications system including DB changes, back-end API and front-end.
				\item \small Built an admin dashboard from scratch including front-end (React) and back-end API (Node).
				\end{itemize}
			}
		}
		\cventry{Fall 2014}{Software Developer}{\href{http://extremeinnovations.com}{Extreme Innovations}}{}{}{
			{\footnotesize
				\begin{itemize}
				\item \small Built \href{http://crowdfind.net}{Crowdfind} (\textbf{\color{see} \href{http://crowdfind.net}{crowdfind.net}}) -- an analytics and discovery platform for crowdfunding projects.
				\item \small Built from scratch in Rails. Features developed: algorithm to retrieve relevant news, daily scrape jobs for data, RickshawJS graphs, responsive design, Google Maps API to map popular projects.
				\end{itemize}
			}
		}
		\cventry{Winter 2014}{Software Developer}{\href{http://nthgensoftware.com}{NthGen Software}}{}{}{
			{\footnotesize
				\begin{itemize}
				\item \small Worked on a high-traffic car auctioning platform called \href{http://traderev.com}{Traderev} (\textbf{\color{see} \href{http://traderev.com}{traderev.com}})
				\item \small Tasks: prevent account sharing using Redis, reduced Analytics page load time from 18s to 1s.
				\end{itemize}
			}
		}
		\cventry{Present}{Safety/Systems Lead}{\href{http://www.teamwaterloop.com/}{uWaterloo Hyperloop Team}}{\href{http://www.spacex.com/hyperloop}{SpaceX Hyperloop Pod Competition}}{}{
			{\footnotesize
				\begin{itemize}
				\item \small Placed in the top 22 out of 180 best engineering schools worldwide in Design Competition.
				\end{itemize}
			}
		}


%comment block
\iffalse
\section{\textbf{References}}
\cvitem{\textbullet}{\small``Extremely intelligent and resourceful. A top 5\% Waterloo intern.'' \footnotesize-- co-founder of Extreme Innovations}
\cvitem{\textbullet}{\small{``Truly bright individual with high aspirations. Provides substantial value.'' \footnotesize-- CEO of PumpUp}}
\fi

\section{\textbf{Projects}}
		\cvitem{\textbullet}{\textbf{What Are You Feeling?} \footnotesize{-- built at Yelp Hackathon}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize
				\begin{itemize}
				\item Used scikit-learn to cluster business by vibe (e.g. hipster) to make recommendations.
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{Your Vote} \footnotesize{-- built at Hack The North 2015}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize
				\begin{itemize}
				\item Find out if your Member of Parliament (MP) votes on bills the same way you would.
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{\href{http://gethighered.ca}{GetHighered} {\color{see} \href{http://gethighered.ca}{gethighered.ca}}} \footnotesize{-- student-run startup}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize
				\begin{itemize}
				\item A website that facilitates easy online applications to retail jobs.
				\end{itemize}
			}
		}

				%comment block
		\iffalse
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{{Mixtape}} \footnotesize{-- built at Hack the North 2014}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize
				\begin{itemize}
				\item Compile songs from SoundCloud and Youtube into shareable mixtapes.
				\end{itemize}
			}
		}

		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{Mobile websites for clients -- {\color{see} \href{http://cortelgroup.com}{cortelgroup.com}} \& {\color{see} \href{http://expocity.ca}{expocity.ca}}} \footnotesize{(visit on mobile)}}

		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{BetterCV}  \footnotesize{-- built at MHacks V}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize
				\begin{itemize}
				\item A MEAN app (Mongo, Express, Angular, Node)	for crowdsourced resum\'{e} critiques.
				\end{itemize}
			}
		}
		\fi

		\vspace*{-0.5cm}


\section{\textbf{Education}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{2018}{BASc in Systems Design Engineering}{University of Waterloo}{}{GPA: 4.0}{}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize
				\begin{itemize}
				\item Dean's Honours List--Finished in the \textbf{top 10} of the class for every single term.
				% \item Research: Applying dynamics models to simulate the effects of monetary policy.
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
\cventry{2015}{Machine Learning}{Stanford University (Coursera)}{}{95.7\%}{}
\cventry{2013}{International Baccalaureate Diploma}{Glenforest Secondary School}{}{Avg: 98.6\%}{}

\section{\textbf{Interests}}
		\cvitem{\textbullet}{Hip-hop, basketball, film, quantum physics, soccer, sci-fi, economics, Elon Musk}

\end{document}
%% end of file `page.tex'.